GEE models

### 2017-10-16 doc/manuscript.Rmd
added numbers to abstract

Results: Participants (73% female, 70% with European-ancestry) had their insulin sensitivity and beta cell function decline by 14-27% over 6 years of follow-up. While in unadjusted models there were several NEFA (e.g. 18:1n-7, 20:1n-9, 22:4n-6) that had negative associations with insulin sensitivity, nearly all of these associations were attenuated in fully adjusted models. In adjusted models, total NEFA, 16:0, 18:1n-9, and 18:2n-6 (as concentrations) had significant negative associations with IGI/IR and ISSI-2, while only 20:5n-3 (as mol%) had positive associations with HOMA2-%S.

>>>>

Results: Participants (73% female, 70% with European-ancestry) had their insulin sensitivity and beta cell function decline by 14-27% over 6 years of follow-up. While in unadjusted models there were several NEFA (e.g. 18:1n-7, 20:1n-9, 22:4n-6) that associated with lower insulin sensitivity, nearly all of these associations were attenuated in fully adjusted models. In adjusted models, total NEFA, 16:0, 18:1n-9, and 18:2n-6 (as concentrations) associated with 3.7 to 8.0% lower IGI/IR and ISSI-2, while only 20:5n-3 (as mol%) associated with 7.7% lower HOMA2-%S.
